Global code motion of congruent instructions

### 2017-04-18 paper.tex
add missing commas

Subsequently, it is checked that the side-effects of the computations (if any)
do not intersect with any side-effects between the instructions to be
hoisted/sunk and their hoisting/sinking point. It is also necessary to check if
there are indirect branch targets, e.g., landing pad, case statements, goto
labels etc., along the path because it becomes difficult to prove safety checks
in those cases. In our current implementation we discard candidates on those
paths.

@@

Overall there was only a minor change in the performance numbers with a few improvements 
(429.mcf, 458.sjeng etc.) and a few regressions (447.dealII, 453.povray
etc.). The \gcm{} pass was run twice in the pass pipeline (at -Ofast),
first after EarlyCSE pass, and then after the inliner. Because EarlyCSE removes
local redundancies, \GCM{} would have to analyze less redundant instructions, also
as inliner creates more redundancies, \GCM{} would have more opportunities to move
congruent instructions out of branches.

>>>>

Subsequently, it is checked that the side-effects of the computations (if any)
do not intersect with any side-effects between the instructions to be
hoisted/sunk and their hoisting/sinking point. It is also necessary to check if
there are indirect branch targets, e.g., landing pad, case statements, goto
labels, etc., along the path because it becomes difficult to prove safety checks
in those cases. In our current implementation we discard candidates on those
paths.

@@

Overall there was only a minor change in the performance numbers with a few improvements 
(429.mcf, 458.sjeng, etc.) and a few regressions (447.dealII, 453.povray,
etc.). The \gcm{} pass was run twice in the pass pipeline (at -Ofast),
first after EarlyCSE pass, and then after the inliner. Because EarlyCSE removes
local redundancies, \GCM{} would have to analyze less redundant instructions, also
as inliner creates more redundancies, \GCM{} would have more opportunities to move
congruent instructions out of branches.
